Flatiron cleaning

### 2023-01-06 Rmd/Response to reviewers.Rmd

<!-- study_consort <- study_cohorts %>% -->
<!--   consort_box_add( -->
<!--     "full", 0, 40, cohort_count_adorn(study_cohorts, .full) -->
<!--   ) %>% -->
<!--   consort_box_add( -->
<!--     "exc_flatiron_rec", 0.2, 35, glue::glue( -->
<!--       "{cohort_count_adorn(study_cohorts, excluded1)}<br>  -->
<!--       • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br> -->
<!--       • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis -->
<!--       ") -->
<!--   ) %>% -->
<!--   consort_box_add( -->
<!--     "flatiron_rec", 0, 30, cohort_count_adorn(study_cohorts, flatiron_rec) -->
<!--   ) %>% -->
<!--   consort_box_add( -->
<!--     "exc_study_criteria", 0.2, 25, glue::glue( -->
<!--       "{cohort_count_adorn(study_cohorts, excluded2)}<br>  -->
<!--       • Borderline cases (not invasive ovarian cancer) <br> -->
<!--       • exclude patients whose histology is unknown <br> -->
<!--       • remove chemotherapy only patients <br> -->
<!--       • include patients who received carboplatin +/- taxane +/- Bev in a adj +/- neo settings -->
<!--       ") -->
<!--   ) %>% -->
<!--   consort_box_add( -->
<!--     "study_criteria", 0, 20, cohort_count_adorn(study_cohorts, study_criteria) -->
<!--   ) %>% -->
<!--   consort_box_add( -->
<!--     "exc_missing_data", 0.2, 15, glue::glue( -->
<!--       "{cohort_count_adorn(study_cohorts, excluded3)}<br>  -->
<!--       • exclude the patients who had surgery but we don’t have a date of surgery -> NONE removed anymore <br>  -->
<!--       • remove patients with long gap between surgery and adjuvant start (3 months) -> NONE removed anymore <br>  -->
<!--       • exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded) <br>  -->
<!--       • exclude patients for whose no RDI were available -->
<!--       ") -->
<!--   ) %>% -->
<!--   consort_box_add( -->
<!--     "missing_data", 0, 10, cohort_count_adorn(study_cohorts, missing_data) -->
<!--   ) %>% -->
<!--   consort_box_add( -->
<!--     "exc_standard_care", 0.2, 5, glue::glue( -->
<!--       "{cohort_count_adorn(study_cohorts, excluded4)}<br>  -->
<!--       • exclude patients with more than 1 line as Neo <br>  -->
<!--       • exclude patients with maintenance within their frontline <br>  -->
<!--       • exclude patients with more than 6 cycles in Neo, more than 9 cycles total in upfront chemo or more than 9 cycles in upfront surgery -->
<!--       ") -->
<!--   ) %>% -->
<!--   consort_box_add( -->
<!--     "Frontline", 0, 0, cohort_count_adorn(study_cohorts, Frontline) -->
<!--   ) %>% -->

<!--   consort_arrow_add( -->
<!--     end = "exc_flatiron_rec", end_side = "left", start_x = 0, start_y = 35 -->
<!--   ) %>% -->
<!--   consort_arrow_add( -->
<!--     end = "exc_study_criteria", end_side = "left", start_x = 0, start_y = 25 -->
<!--   ) %>% -->
<!--   consort_arrow_add( -->
<!--     end = "exc_missing_data", end_side = "left", start_x = 0, start_y = 15 -->
<!--   ) %>% -->
<!--   consort_arrow_add( -->
<!--     end = "exc_standard_care", end_side = "left", start_x = 0, start_y = 5 -->
<!--   ) %>% -->
<!--   consort_arrow_add( -->
<!--     end = "Frontline", end_side = "top", start_x = 0, start_y = 40 -->
<!--   ) -->

<!-- study_consort %>% -->
<!--   ggplot() +  -->
<!--   geom_consort() + -->
<!--   theme_consort(margin_h = c(1,6), margin_v = c(0,30)) -->
<!-- ``` -->
<!-- <br> -->
<!-- ```{r} -->
<!-- practice %>%  -->
<!--   # Limit to the patietns after exclusion criteria -->
<!--   filter(str_detect(PatientID, paste(Frontline$patientid, collapse = "|"))) %>%  -->
<!--   select(PracticeType) %>% -->
<!--   tbl_summary() -->
<!-- ``` -->
<!-- <br> -->

<!-- *** -->

# II.Data analysis
## Explore the dataset

```{r exploratory data analysis}
full_data_study_pop <-
  Treatment %>%
  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>%
  arrange(patientid, episodedate, drugname) %>% 
  filter(had_carbo == "Yes") %>% 
  filter(linenumber_adj == 1)

```

<!-- ### Number of cycle received by patients in our study population -->

<!-- <span style="color:green">**Table supp X Number of cycle in Neo**</span> -->
<!-- ```{r} -->
<!-- full_data_study_pop %>% -->
<!--   filter(chemotherapy_type == "Neoadjuvant") %>% -->
<!--   arrange(desc(cycle_increment)) %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(cycle_increment) %>% -->
<!--   tbl_summary() -->
<!-- full_data_study_pop %>% -->
<!--   filter(chemotherapy_type == "Neoadjuvant") %>% -->
<!--   arrange(desc(cycle_increment)) %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(cycle_increment) %>% -->
<!--   tbl_summary(type = list(cycle_increment ~ "continuous")) -->

<!-- full_data_study_pop %>% -->
<!--   filter(chemotherapy_type == "Neoadjuvant") %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(linename) %>% -->
<!--   tbl_summary() -->
<!-- ``` -->

<!-- <span style="color:green">**Table supp X Number of cycle in Adj**</span> -->
<!-- ```{r} -->
<!-- full_data_study_pop %>% -->
<!--   filter(chemotherapy_type == "Adjuvant") %>% -->
<!--   arrange(desc(cycle_increment)) %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(cycle_increment, therapy) %>% -->
<!--   tbl_summary(by = therapy) -->
<!-- full_data_study_pop %>% -->
<!--   filter(chemotherapy_type == "Adjuvant") %>% -->
<!--   arrange(desc(cycle_increment)) %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(cycle_increment, therapy) %>% -->
<!--   tbl_summary(by = therapy, -->
<!--               type = list(cycle_increment ~ "continuous")) -->

<!-- full_data_study_pop %>% -->
<!--   filter(chemotherapy_type == "Adjuvant") %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(linename, therapy) %>% -->
<!--   tbl_summary(by = therapy) -->
<!-- ``` -->
<!-- <br> -->
<br>

***

# Clinical Analysis
## 1.Clinical summary table

<!-- <span style="color:green">**Table X Overall summary demographic/clinical data**</span> -->
<!-- ```{r Table 1} -->
<!-- Frontline %>%  -->
<!--   select(c(vital, raceeth,  -->
<!--            agecat, "ageatdx", -->

<!--            bmi_at_dx, bmi_cat,  -->
<!--            weight_at_dx, height_at_dx, bsa_at_dx, -->

<!--            histology1, "histology", "stagecat", imp_stagecat, -->

<!--            "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor", -->
<!--            "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown")) %>%  -->
<!--   tbl_summary() %>% bold_labels() -->
<!-- ``` -->

<!-- <span style="color:green">**Table X Summary demographic/clinical data by race**</span> -->
<!-- ```{r Table 2} -->
<!-- Frontline %>%  -->
<!--   select(c(raceeth, "vital", -->
<!--            agecat, "ageatdx", -->

<!--            "bmi_at_dx", bmi_cat, "BSA", -->
<!--            "stagecat", imp_stagecat)) %>%  -->
<!--   tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05) -->
<!-- ``` -->
<!-- <br> -->

## <span style="color:green">**Table 1 Summary demographic/clinical data by bmi**</span>
```{r Table 3}
Frontline <- Frontline %>% 
  mutate(year_diagnosis = year(Frontline$diagnosisdate)) %>% 
  mutate(dx_year_cat = case_when(
    year_diagnosis %in% c(2011, 2012, 2013, 2014, 2015)        ~ "2011-2015",
    year_diagnosis %in% c(2016, 2017, 2018)                    ~ "2016-2018",
    year_diagnosis %in% c(2019, 2020, 2021)                    ~ "2019-2021"
  ))

summary(Frontline$year_diagnosis)
table(Frontline$year_diagnosis)
table(Frontline$dx_year_cat)

Frontline %>% 
  select(c(dx_year_cat, month_at_os, month_at_os_from_treatment,
           raceeth, "vital",
           agecat, "ageatdx",
            histology1, "histology",
           "bmi_at_dx", bmi_cat, "BSA",
           "stagecat", imp_stagecat,
           therapy, debulking, imp_debulking)) %>% 
  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)

Frontline %>% 
  select(c(dx_year_cat, 
           therapy)) %>% 
  tbl_summary(by = therapy) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)

```
<br>
<br>

***

<br>

# II.Treatment Analysis

<!-- ## 1.Treatment summary table -->

<!-- <span style="color:green">**Table X Summary treatment data by race**</span> -->
<!-- ```{r Table 4} -->
<!-- Frontline %>%  -->
<!--   select(c(raceeth, -->
<!--            "debulking", imp_debulking , "therapy" -->
<!--            )) %>%  -->
<!--   tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05) -->
<!-- ``` -->
<!-- <br> -->

<!-- <span style="color:green">**Table X Summary treatment data by bmi**</span> -->
<!-- ```{r Table 5} -->
<!-- Frontline %>%  -->
<!--   select(c(bmi_cat, -->
<!--            "debulking", imp_debulking, "therapy" -->
<!--            )) %>%  -->
<!--   tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05) -->
<!-- ``` -->

<!-- ## <span style="color:green">**Table S0 Summary of the expected, actual dose, and RDI, Crcl, ...**</span> -->
<!-- Here we calculated the mean of amount, CrCl, BSA, height, weight, creatinine, -->
<!--          target_auc, expected_dose, dose received,  -->
<!--          RDI per patient/therapy/settings for each drug name.   -->
<!-- The tables show the median IQR for carboplatin calculated over patients with the same therapy (Upfront C or S) and setting (Neo or Adj). -->
<!-- ```{r Summary of the expected, actual dose, and RDI} -->
<!-- tbl <- full_data_study_pop %>%  -->
<!--   # Treatment %>%  -->
<!--   # # Limit to the patietns after exclusion criteria -->
<!--   # filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>%  -->
<!--   # arrange(patientid, episodedate, drugname) %>%  -->
<!--   # # group to have RDI by cycle for each drug  -->
<!--   # # group_by(patientid, chemotherapy_type, cycle_increment, drugname) %>% -->
<!--   # # mutate(mean_RDI_per_cycledrug = round(mean(relative_dose_intensity, na.rm = TRUE), 3) -->
<!--   # # ) %>%  -->
<!--   # # ungroup() %>%  -->
<!--   # filter(drugname == "carboplatin") %>%  -->
<!--   # filter(linenumber_adj == 1) %>%  -->

<!--   group_by(patientid, therapy, chemotherapy_type, drugname) %>%  -->
<!--   summarise(amount = mean(amount, na.rm = TRUE),  -->
<!--             BSA = mean(BSA),  -->
<!--             height = mean(height),  -->
<!--             weight = mean(weight),  -->
<!--             creatinine = mean(creatinine), -->
<!--             CrCl = mean(CrCl), -->
<!--             target_auc = mean(target_auc), -->
<!--             expected_dose = mean(expected_dose), -->
<!--             relative_dose_intensity = mean(mean_RDI_per_drug)) %>%  -->
<!--   ungroup() %>%  -->
<!--   mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant"))) -->

<!-- tbl %>% filter(drugname == "carboplatin" & therapy == "Upfront Chemo") %>%  -->
<!--   select(amount, CrCl, BSA, height, weight, creatinine, -->
<!--          target_auc, expected_dose, "dose received" = amount,  -->
<!--          "RDI" = relative_dose_intensity, chemotherapy_type) %>%  -->
<!--   tbl_summary(by = chemotherapy_type) %>% bold_labels() %>% -->
<!--   modify_caption("**Upfront Chemo**") -->

<!-- tbl %>% filter(drugname == "carboplatin" & therapy == "Upfront Surgery") %>%  -->
<!--   select(amount, CrCl, BSA, height, weight, creatinine, -->
<!--          target_auc, expected_dose, "dose received" = amount,  -->
<!--          "RDI" = relative_dose_intensity) %>%  -->
<!--   tbl_summary() %>% bold_labels() %>% -->
<!--   modify_caption("**Upfront Surgery**") -->
<!-- ``` -->
<!-- <br> -->

<!-- <!-- ## 2.Treatment Plots --> -->

<!-- ```{r treatment plots} -->
<!-- full_data_study_pop %>%  -->
<!--   filter(chemotherapy_type == "Neoadjuvant") %>%  -->
<!--   distinct(patientid, .keep_all = TRUE) %>%  -->
<!--   select(linename) %>%  -->
<!--   tbl_summary(label = list(linename ~ "line name received as Neoadujant")) -->
<!-- full_data_study_pop %>%  -->
<!--   filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>%  -->
<!--   distinct(patientid, .keep_all = TRUE) %>%  -->
<!--   select(linename, therapy) %>%  -->
<!--   tbl_summary(by = therapy, -->
<!--               label = list(linename ~ "line name received as Adjuvant")) -->
<!-- ``` -->
<!-- <br> -->

<!-- ## 3.Survivals by treatment -->

<!-- <div class = "row"> -->
<!-- <div class = "col-md-6"> -->
<!-- ```{r treatment survival, fig.height = 7} -->
<!-- ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ 1, data=Frontline %>%  -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of diagnosis",  -->
<!--            font.main = c(24, "bold", "black"),  -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),  -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),  -->
<!--            size = 1.5, -->

<!--            pval=TRUE,  -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"),  -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)"  -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

<!-- ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ debulking, data=Frontline %>% -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of diagnosis", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

### 2023-01-06 Rmd/Response to reviewers.Rmd

<!-- ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ imp_debulking, data=Frontline %>% -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of diagnosis", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

<!-- # OS by therapy -->
<!-- ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ therapy, data=Frontline %>%  -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of diagnosis",  -->
<!--            font.main = c(24, "bold", "black"),  -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),  -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),  -->
<!--            size = 1.5, -->

<!--            pval=TRUE,  -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"),  -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)"  -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->
<!-- ``` -->
<!-- </div> -->

<!-- <div class = "col-md-6"> -->
<!-- ```{r, fig.height = 7} -->
<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ 1, data=Frontline %>%  -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of from first treatment",  -->
<!--            font.main = c(24, "bold", "black"),  -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),  -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),  -->
<!--            size = 1.5, -->

<!--            pval=TRUE,  -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"),  -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)"  -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ debulking, data=Frontline %>% -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of from first treatment", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ imp_debulking, data=Frontline %>% -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of from first treatment", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

<!-- # OS by therapy -->
<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ therapy, data=Frontline %>%  -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of from first treatment",  -->
<!--            font.main = c(24, "bold", "black"),  -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),  -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),  -->
<!--            size = 1.5, -->

<!--            pval=TRUE,  -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"),  -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)"  -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->
<!-- ``` -->
<!-- </div> -->
<!-- </div> -->

<br>
<br>

***

<br>

# III.RDI
RDI is calculated by drug so 1 for each Carboplatin, Cisplatin, Oxaloplatin, Paclitaxel, Paclitaxel protein bound, Docetaxel.

```{r echo=TRUE}
# RDI_grp = case_when(
#     mean_RDI_per_drug >= 0.85              ~ "adequate",
#     mean_RDI_per_drug < 0.85               ~ "underdose"
#   ))
```
Start with plotting :

<!-- ## 1.Plots RDI -->
<!-- ## <span style="color:green">**Figure 1: Ridge**</span>   -->
<!-- ```{r ggridges, fig.width=16, fig.height=18} -->
<!-- library(ggridges) -->
<!-- # Frontline %>%  -->
<!-- #   pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>%  -->
<!-- #   filter(!is.na(value)) %>%  -->
<!-- #   ggplot(aes(y=raceeth, x=value,  fill=raceeth -->
<!-- #              )) + -->
<!-- #     geom_density_ridges(alpha=0.5) + -->
<!-- #     theme_ridges()+ -->
<!-- #   theme(#text = element_text(size = 14),#axis.text.y = element_blank(), -->
<!-- #         panel.spacing = unit(0.1, "lines"), -->
<!-- #         strip.text.x = element_text(size = 14) -->
<!-- #     ) + -->
<!-- #   geom_vline(xintercept = 1, color = "red", linetype = 2)+ -->
<!-- #   geom_vline(xintercept = 0.85, color = "blue", linetype = 2)+ -->
<!-- #  -->
<!-- #   facet_wrap(therapy ~ name, ncol = 2, scales = "free_x") -->

<!-- Frontline %>%  -->
<!--   pivot_longer(cols = c(RDI_carbo_neo, RDI_carbo_adj), -->
<!--                values_to = "RDI") %>%  -->
<!--   filter(!is.na(RDI)) %>%  -->
<!--   ggplot(aes(y=bmi_cat, x=RDI,  fill=bmi_cat -->
<!--              )) + -->
<!--     geom_density_ridges(alpha=0.5) + -->
<!--     theme_ridges()+ -->
<!--   theme(#text = element_text(size = 14),#axis.text.y = element_blank(), -->
<!--         panel.spacing = unit(0.1, "lines"), -->
<!--         strip.text.x = element_text(size = 14) -->
<!--     ) + -->
<!--   geom_vline(xintercept = 1, color = "red", linetype = 2)+ -->
<!--   geom_vline(xintercept = 0.85, color = "blue", linetype = 2)+ -->

<!--   facet_wrap(therapy ~ name, ncol = 1) -->
<!-- ``` -->

## 2.RDI summary table

```{r}
my_theme <-
  list(
    # Some gt customization
    "as_gt-lst:addl_cmds" = list(
      # make the font size small
      tab_spanner = rlang::expr(gt::tab_options(row.striping.background_color = "lightgrey",
                                                row.striping.include_stub = TRUE,
                                                row.striping.include_table_body = TRUE,
                                                row_group.border.top.color = "blue",
                                                # table.background.color = "white", 
                                                heading.background.color = "lightblue", 
                                                # column_labels.background.color = "orange", 
                                                row_group.background.color = "grey",
                                                stub.background.color = "slateblue", 
                                                summary_row.background.color = "tomato", 
                                                grand_summary_row.background.color = "green")),
      # add a custom title and subtitle to every table
      # user_added1 = rlang::expr(gt::tab_header(
      #   title = "Christelle's Table", subtitle = "Yeap"))#,
      # add a custom data source note
      # user_added2 = rlang::expr(gt::tab_source_note(
      #   source_note = "Source: our data!"))#,
      # stripe the table rows
      user_added1 = rlang::expr(gt::opt_row_striping())#,
      # user_added4 = rlang::expr(gt::opt_table_lines("none"))
      )
    )

reset_gtsummary_theme()
set_gtsummary_theme(my_theme)
```

<br>

## <span style="color:green">**Table 2: Summary RDI data by race and bmi**</span>  
Platin  
```{r Table 7 Summary RDI data by race and bmi}
Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c("RDI Neo" = RDI_carbo_neo, "RDI Neo cat" = RDI_carbo_neo_grp,
           "RDI Adj" = RDI_carbo_adj, "RDI Adj cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary() %>%
  bold_labels() %>% 
  modify_caption("**Upfront Chemo**")

Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c("RDI Neo cat" = RDI_carbo_neo_grp,
           "RDI Adj cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = "RDI Adj cat") %>%
  bold_labels() %>% add_overall() %>% 
  modify_caption("**Upfront Chemo**") %>% 
  modify_spanning_header(all_stat_cols() ~ "**RDI Adj cat**")

tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(raceeth, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05) %>% add_overall()
tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05) %>% add_overall()

tbl3 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(raceeth, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05) %>% add_overall()
tbl4 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05) %>% add_overall()

tbl7 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI")) %>%
  modify_caption("**Upfront Chemo**")
tbl8 <-
  tbl_merge(list(tbl3, tbl4))
tbl_stack(list(tbl7, tbl8),
          group_header = c(
                           "carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo"),
          quiet = TRUE)

tbl5 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
  select(c(raceeth, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05) %>% add_overall()
tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05) %>% add_overall()

tbl_merge(list(tbl5, tbl6), tab_spanner = c("Race/Ethnicity", "BMI")) %>%
  modify_caption("**Upfront Surgery**")
```
<br>
<br>

***

<br>

<!-- ## 3.Survivals by RDI -->
<!-- ### Survivals RDI by chemotherapy type -->
<!-- ### <span style="color:green">**Figure 2: KM 3 panel figure**</span>   -->

<!-- ```{r OS treatment RDI, fig.height = 7} -->
<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo_grp,  -->
<!--                    data=Frontline %>%  -->
<!--                      filter(therapy == "Upfront Chemo") %>% -->
<!--                      distinct(patientid, .keep_all = TRUE) -->
<!--                    ), -->
<!--            title = "OS from treatment carboplatin \nUpfront Chemo", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->
